\Large \bf Lissy: Experimenting with on-chain order books

### 2022-06-02 LaTeX-LNCS-2022/sections/paper.tex
small changes

In \cm, both the tokens and ETH that a trader wants to potentially use in the order book are preloaded into the contract. We discuss some alternative designs in~\cite{https://doi.org/10.48550/arxiv.2101.06291}.

@@

Imagine you have just launched a token on Ethereum. Now you want to be able to trade it. While the barrier to entry for exchange services is low, it still exists. For a centralized or decentralized exchange, you have to convince the operators to list your token and you will be delayed while they process your request. For an automated market maker, you will have to lock up a large amount of ETH into the DApp, along with your tokens. For roll-ups, you will have to host your own servers. By contrast to all of these, with an on-chain order book, you just deploy the code alongside your token and trading is immediately supported. This should concern regulators. Even if it is too slow today, there is little reason for developers not to offer it as a fallback solution that accompanies every token. With future improvements to blockchain scalability, it could become the de facto trading method.

>>>>

In \cm, both the tokens and ETH that a trader wants to potentially use are preloaded into the contract. We discuss alternative designs in~\cite{https://doi.org/10.48550/arxiv.2101.06291}.

@@

Imagine you have just launched a token on Ethereum. Now you want to be able to trade it. While the barrier to entry for exchange services is low, it still exists. For a centralized or decentralized exchange, you have to convince the operators to list your token and you will be delayed while they process your request. For an automated market maker, you will have to lock up a large amount of ETH into the DApp, along with your tokens. For roll-ups, you will have to host your own servers. By contrast to all of these, with an on-chain order book, you just deploy the code alongside your token and trading is immediately supported. Even if it is too slow today, there is little reason for developers not to offer it as a fallback solution that accompanies every token. With future improvements to blockchain scalability, it could become the de facto trading method.
